### 2013-02-15 doc/icml2013/algo.tex
checked in

@@

% Method of moments interpretation
%Though we have motivated Spectral Experts using regression on powers
%of $y$ given powers of $x$,
%we can also think of the algorithm in terms of
%the method of moments.  Specifically,
%the optimality conditions for the regression of $M_2$ and $M_3$ are:
%\begin{align}
%\E[x\tp{2} (\innerp{M_2}{x\tp{2}} + \sigma^2 - y^2)] = 0, \\
%\E[x\tp{3} (\innerp{M_3}{x\tp{3}} + 3 \sigma^2 \innerp{M_1}{x} - y^3)] = 0.
%\end{align}

@@

\subsection{Identifiability from moments}

The mixture of linear regressions model is identifiable subject to
permutations of the components\citationneeded. However, our approach
employs regression on $x\tp{2}$ and $x\tp{3}$, and thus requires
$\mathcal{X} \otimes \mathcal{X}$ and $\mathcal{X} \otimes \mathcal{X}
\otimes \mathcal{X}$ to be linearly independent modulo symmetry. We call
these condition {\em quadratic} and {\em cubic} independence.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Theoretical results}

@@

% Method of moments interpretation
% This is garbage
%Though we have motivated Spectral Experts using regression on powers
%of $y$ given powers of $x$,
%we can also think of the algorithm in terms of
%the method of moments.  Specifically,
%the optimality conditions for the regression of $M_2$ and $M_3$ are:
%\begin{align}
%\E[x\tp{2} (\innerp{M_2}{x\tp{2}} + \sigma^2 - y^2)] = 0, \\
%\E[x\tp{3} (\innerp{M_3}{x\tp{3}} + 3 \sigma^2 \innerp{M_1}{x} - y^3)] = 0.
%\end{align}

@@

\subsection{Identifiability}

In ordinary linear regression, the regression coefficients are identifiable
only if the data has full rank: $\E[x\tp{2}] \succ 0$.
However, in mixture of linear regressions.

The mixture of linear regressions model is identifiable subject to
permutations of the components. However, our approach
employs regression on $x\tp{2}$ and $x\tp{3}$, and thus requires
$\mathcal{X} \otimes \mathcal{X}$ and $\mathcal{X} \otimes \mathcal{X}
\otimes \mathcal{X}$ to be linearly independent modulo symmetry. We call
these condition {\em quadratic} and {\em cubic} independence.
